### 2022-08-06 latex/Chapters/Puzzles.tex
update

Up to rotations of the full RC, there are $\frac{8! * 3^{7}}{24}$ = 3,674,160 possible combinations. Indeed, there are 8 possible ways of choosing the position of the eight corner cubies (since there are known algorithms, such as R’ U R’ D2 R U’ R’ D2 R2, to swap exactly two and only two adjacent corners). Now each of the corner cubies can be oriented in 3 different ways (not 6, since as discussed earlier, the clock-wise order of a given corner cubie cannot be changed), so that gives us $3^8$ permutations of the corners orientation. However, the \textit{corner orientation parity} (\textbf{COP}) (see \cite{Schoenert} for details) must be equal to 0 modulo 3, and hence why only one third of all these $3^8$ permutations are attainable. Finally, the denominator of 24 is due to the equivalence by whole cube rotation as also discussed in the previous section.
\\
The insight and knowledge of this section will be useful for me to implement \textit{perfect scrambling} for the 2x2x2 RC. Indeed, the way I generate perfectly shuffled RCs is by randomly placing the 8 corners, then randomly choose the orientation of each of the first 7 corners, and finally fixing the $8^{th}$ corner's orientation so that the COP be equal to 0 \% 3.

>>>>

Up to rotations of the full RC, there are $\frac{8! * 3^{7}}{24}$ = 3,674,160 possible combinations. Indeed, there are 8! possible ways of choosing the position of the eight corner cubies (since there are known algorithms, such as R’ U R’ D2 R U’ R’ D2 R2, to swap exactly two and only two adjacent corners), each of which can be oriented in 3 different ways (not 6, since as discussed earlier, the clock-wise order of a given corner cubie can never be changed). That gives us $3^8$ permutations of the corners orientation. However, the \textit{corner orientation parity} (\textbf{COP}) (see \cite{Schoenert} for details) is invariant (\% 3) by any legal move of the RC. Since rotating by $120^{o}$ a given corner cubie increases the COP by 1, we conclude that only one third of all these $3^8$ permutations are attainable (namely those for which the COP is equal to 0 \% 3). Finally, the denominator of 24 is due to the equivalence by whole cube rotation as discussed in the previous section.
\\
The insight and knowledge of this section will be useful for me to implement \textit{perfect scrambling} for the 2x2x2 RC. Indeed, the way I generate perfectly shuffled RCs is by randomly placing the 8 corners, then randomly choosing the orientation of the first 7, and finally fixing the $8^{th}$ corner's orientationto make COP equal to 0 \% 3.
